
# Perform analyses on response variables and DDM parameters

```{r}
# detach("package:plotly", unload=TRUE)
rm(list = ls())
source("../analysis_funcs.R")

statslist = list()

WD = '../../data'
WDD = file.path(WD, 'experiment')
mytheme = theme_classic(base_size = 11) + theme(legend.position = 'bottom', legend.title = element_blank())
theme_set(mytheme)
# Load previous fit
#MYFILE = '../results/linear_drift_no_pooling_corr_ddm-processed_data_censored-27-12-2023_07:59-10000-50000-jags-pars.RData'
#MYFILE = '../results/linear_drift_no_pooling_bd_ddm-processed_data_censored-27-12-2023_20:07-10000-50000-jags-pars.RData'
init100 = F
if (init100) {
  MYFILE = '../results/linear_drift_no_pooling_ddm-processed_data_censored_100-22-12-2023_21:49-10000-50000-jags-pars.RData'
load(MYFILE)
load(file.path(WDD, "processed_data_censored_100.RData"))

} else {
  MYFILE = '../results/linear_drift_no_pooling_ddm-processed_data_censored-22-12-2023_23:53-10000-50000-jags-pars.RData'
load(MYFILE)
load(file.path(WDD, "processed_data_censored.RData"))

}

numSubjs = dataList$N

# Load data
#load(file.path(WDD, "processed_data_censored_220.RData"))

grouping_var = 'subj_context'
choicedata.common$subj_context = paste(choicedata.common$subjID, choicedata.common$context)
dataList = organize_data(choicedata.common, grouping_var, long = T)
subjList <-
  unique(choicedata.common[c('subjID',
                             'context',
                             'context_num',
                             'context_order',
                             'background_col',
                             grouping_var)])

choicedata.common = choicedata.common %>% mutate(
  Context = ifelse(context == 'c1', 'High volatility', 'Low volatility'),
  Choice = ifelse(choice == 1, 'Later option', 'Immediate option'),
  Context_order = ifelse(context_order == 1, 'First context', 'Second context'),
  Group =  ifelse(
    context_order == 1 &
      context == 'c1' |
      context_order == 2 & context == 'c2' ,
    'High vol. first',
    'Low vol. first'
  )
)

ratingdata.sub = ratingdata.sub %>% mutate(
  Context = ifelse(context == 'c1', 'High volatility', 'Low volatility'),
  Context_order = ifelse(context_order == 1, 'First context', 'Second context'),
  Group =  ifelse(
    context_order == 1 &
      context == 'c1' |
      context_order == 2 & context == 'c2' ,
    'High vol. first',
    'Low vol. first'
  )
)
#ratingdata.sub = ratingdata.sub %>% arrange(subjID, key.rt) %>% group_by(subjID, Context, Context_order, Group) %>% mutate(key.rt = key.rt - lag(key.rt), key.rt.orig = key.rt) 
```

# Extract parameters
```{r}

numPars <- 5
# Individual parameters (e.g., individual posterior means)
allIndPars <- array(NA, c(numSubjs, numPars))
allIndPars <- as.data.frame(allIndPars)
#parVals$boundary.p = parVals$noise.p
#parVals$bias.p = parVals$SNR.p
for (i in 1:numSubjs) {
  allIndPars[i,] <- c(
    mean(parVals$b.drift.intercept.p[i,]),
    mean(parVals$b.drift.amount.p[i,]),
    mean(parVals$bias.p[i,]),
    mean(parVals$nondectime.p[i,]),
    mean(parVals$noise.p[i,])
  )
}

allIndPars = cbind(allIndPars, subjList[-ncol(subjList)])

colnames(allIndPars) <- c(
  "b.drift.intercept.p",
  "b.drift.amount.p",
  "bias.p",
  "nondectime.p",
  "noise.p",
  "subjID",
  "context",
  "context_num",
  "context_order",
  "background_col"
)

allIndPars = allIndPars %>% mutate(
  Context = ifelse(context == 'c1', 'High volatility', 'Low volatility'),
  Context_short = ifelse(context == 'c1', 'High', 'Low'),
  Context_order = ifelse(context_order == 1, 'First context', 'Second context'),
  Group =  ifelse(
    context_order == 1 &
      context == 'c1' |
      context_order == 2 & context == 'c2' ,
    'High vol. first',
    'Low vol. first'
  )
)
```

# Remove subjects if they have low sensitivity
```{r}
Rhat = max(myfit_summary[, 'psrf'])
print(Rhat)

g = grep("b.drift.amount.p\\[", rownames(myfit_summary))
allIndPars$lower_bound = myfit_summary[g, 'Lower95']
allIndPars$upper_bound = myfit_summary[g, 'Upper95']
allIndPars$Median = myfit_summary[g, 'Median']
allIndPars$b.drift.amount.p.0 = allIndPars$lower_bound > 0 |
  allIndPars$upper_bound < 0

plot(
  allIndPars$lower_bound[order(allIndPars$lower_bound)],
  type = 'l',
  ylim = c(min(allIndPars$lower_bound), max(allIndPars$upper_bound)),
  xlab = "Subject/Context",
  ylab = "5%-quantile for drift sensitivity"
)
#lines(allIndPars$upper_bound[order(allIndPars$lower_bound)]  , type = 'l')
abline(0, 0, col = 'red')
```

# Keep only subjects with a significant relationship between drift and value
```{r, fig.width = 15}
allIndPars$index = seq(nrow(allIndPars))

allIndPars.subj = allIndPars %>% group_by(subjID) %>% summarise(keep = max(lower_bound) > 0) %>% filter(keep) %>% ungroup()
include_subjects = allIndPars.subj$subjID

allIndPars.sub = subset(allIndPars, subjID %in% include_subjects)

write.table(include_subjects, file = file.path(WDD, 'final_subjects_included.txt'), row.names = F, col.names=F, quote = F)
```

# Remove outliers
```{r}
#allIndPars = allIndPars %>% filter(nondectime.p < 2)
```



# Group distributions for parameters
```{r}
for (var in c("context",  "background_col", "context_order"))
{
  get_par_jags("b.drift.intercept.p", var)
  get_par_jags("b.drift.amount.p", var)
  get_par_jags("bias.p", var)
  get_par_jags("nondectime.p", var)
  get_par_jags("noise.p", var)

  }

get_par_jags("b.drift.intercept.p", var2 = "Context", var = "context_order")
get_par_jags("b.drift.amount.p", var2 = "Context", var = "context_order")
get_par_jags("bias.p", var2 = "Context", var = "context_order")
get_par_jags("nondectime.p", var2 = "Context", var = "context_order")
get_par_jags("noise.p", var2 = "Context", var = "context_order")

context_sigmas = c(5, 2, 1)

allIndPars$context_sigma = context_sigmas[allIndPars$context_num]

mypars = c("b.drift.intercept.p",
           "b.drift.amount.p",
           "bias.p",
           "nondectime.p",
           "noise.p")

for (mypar in mypars) {
  print("------------------------------------")
  print(mypar)
  myform = formula(paste(
    mypar,
    "context + context_order + (1|subjID)", #  + background_col
    sep = "~"
  ))
  model = lmer(myform, data = allIndPars %>% filter(subjID %in% include_subjects))
  print(summary(model))
} 
```


# Plot RTs in relation to estimated subjective value
```{r}
source('./RTanalysis.R')
```

# Check distribution of context order and context
```{r}
choicedata.order = choicedata %>% group_by(subjID) %>% slice_head(n=1) 
choicedata.order = choicedata.order %>% group_by(Context, context, context_order, Context_order) %>% summarise(size = n())
print(choicedata.order)
```

# Check response probabilities
```{r}
source('./ChoiceAnalysis.R')
```


# Plot ratings
```{r}
source('./RatingAnalysis.R')
```

# Difference in ratings vs difference in DDM parameters
```{r}

rating_par_names = c("bid.diff" = "WTP range",
                     "key.rt" = "WTP response time",
                     "bid.rt.max" = "Max response time")
choice_par_names = c(
  "b.drift.intercept.p" = "Drift intercept",
  "b.drift.amount.p" = "Drift sensitivity",
  "noise.p" = "Noise",
  "bias.p" = "Bias",
  "nondectime.p" = "Non-decision time",
  "sigma.p" = "Drift sd"
)
# Check differences

ratingdata.high <- ratingdata %>% 
  filter(context == 'c1')
ratingdata.low <- ratingdata %>% 
  filter(context == 'c2')

cols <- c("subjID", "ev", "amount_later", "b.drift.intercept.p", "key.rt",
  "b.drift.amount.p", "bias.p", "nondectime.p", "noise.p", "bid.diff", "Group")

ratingdata.all <- merge(ratingdata.high[cols], ratingdata.low[cols], by = c('subjID', 'ev', 'amount_later'), suffix = c('.high', '.low')) 

# compute differences high vs low
ratingdata.all <- ratingdata.all %>% mutate(
  key.rt = key.rt.high - key.rt.low, bid.diff = bid.diff.high - bid.diff.low, 
  b.drift.amount.p = b.drift.amount.p.high - b.drift.amount.p.low,
  b.drift.intercept.p = b.drift.intercept.p.high - b.drift.intercept.p.low,
  nondectime.p = nondectime.p.high - nondectime.p.low,
  noise.p = noise.p.high - noise.p.low,
  bias.p = bias.p.high - bias.p.low
  ) %>% mutate(Group = Group.low)

mypars.rating = c("bid.diff", "key.rt") # , "bid.rt.max")
main.mat = inter.mat =  NULL
for (mypar.rating in mypars.rating) {
  for (co in c("High vol. first", "Low vol. first")) {
    for (mypar in mypars) {
      myformula = as.formula(
        sprintf(
          "%s ~ scale(%s)*scale(amount_later) + (1| subjID)",
          mypar.rating,
          mypar
        )
      )
      model = lmer(myformula, data = ratingdata.all %>% filter(Group == co))
      ss = summary(model)
      print(myformula)
      print(ss)
      ss.1 = coef(ss)[sprintf("scale(%s)", mypar), c("Estimate", "t value", "df", "Pr(>|t|)")]
      ss.2 = coef(ss)[sprintf("scale(%s):scale(amount_later)", mypar), c("Estimate", "t value", "df", "Pr(>|t|)")]
      main.mat = rbind(main.mat, c(mypar.rating, mypar, co, round(ss.1, 3)))
      inter.mat = rbind(inter.mat, c(mypar.rating, mypar, co, round(ss.2, 3)))
  }
}
}
main.mat = as.data.frame(main.mat)
inter.mat = as.data.frame(inter.mat)

main.mat = as.data.frame(main.mat)
inter.mat = as.data.frame(inter.mat)
main.mat = main.mat %>% arrange(V1, V2)
inter.mat = inter.mat %>% arrange(V1, V2)
main.mat = main.mat %>% mutate(V1 = rating_par_names[as.character(V1)], V2 = choice_par_names[as.character(V2)])
inter.mat = inter.mat %>% mutate(V1 = rating_par_names[as.character(V1)], V2 = choice_par_names[as.character(V2)])

colnames(main.mat) = colnames(inter.mat) = c("WTP parameter",
                                             "DDM parameter",
                                             "Group",
                                             "Estimate",
                                             "t",
                                             "df",
                                             "p-value")
main.mat = main.mat %>% relocate(Group) %>% arrange(`Group`, `WTP parameter`,
                                             `DDM parameter`,
                                             )
inter.mat = inter.mat %>% relocate(Group) %>% arrange(`Group`, `WTP parameter`,
                                             `DDM parameter`,
                                             )

View(main.mat)
View(inter.mat)

statslist['_table_diff_main_'] = tab_to_str(main.mat)
statslist['_table_diff_inter_'] = tab_to_str(inter.mat)

# myplot = ggplot(data = ratingdata.all, aes(x = amount_later, y = key.rt, group = subjID, color=Group.high)) +
#   geom_line() +
#   geom_point() +
#   xlab('Drift sensitivity difference (high vol. - low vol.)') +
#   ylab('Response time difference (high vol. - low vol.)') 
# print(myplot)
# 
# ratingdata.mean =  ratingdata.all %>% group_by(subjID) %>% summarise(key.rt = mean(key.rt), noise.p = mean(noise.p), b.drift.amount.p = mean(b.drift.amount.p))
#  
# myplot = ggplot(data = ratingdata.mean, aes(x = b.drift.amount.p, y = key.rt)) +
#   geom_point() +
#   xlab('Drift sensitivity difference (high vol. - low vol.)') +
#   ylab('Response time difference (high vol. - low vol.)') 
# print(myplot)
# 
# myplot = ggplot(data = ratingdata.mean, aes(x = noise.p, y = key.rt)) +
#   geom_point() +
#   xlab('Drift sensitivity difference (high vol. - low vol.)') +
#   ylab('Response time difference (high vol. - low vol.)') 
# print(myplot)
 

```

# Rating RT
```{r}
# remove outliers?
source("./RatingRTanalysis.R")

```

# Random slopes of ratings vs DDM parameters

```{r}
rating_par_names = c("bid.diff" = "WTP range",
                     "key.rt" = "WTP response time",
                     "bid.rt.max" = "Max response time")
choice_par_names = c(
  "b.drift.intercept.p" = "Drift intercept",
  "b.drift.amount.p" = "Drift sensitivity",
  "noise.p" = "Noise",
  "bias.p" = "Bias",
  "nondectime.p" = "Non-decision time",
  "sigma.p" = "Drift sd"
)

myplots.list = list()
j = 1
main.mat = inter.mat = NULL
#*Group*Context
mypars.rating = c("bid.diff", "key.rt") # , "bid.rt.max")
for (mypar.rating in mypars.rating) {
  for (mypar in mypars) {
    for (co in c(1, 2)) {
      myformula = as.formula(
        sprintf(
          "%s ~ scale(%s)*scale(amount_later) + (1| subjID)",
          mypar.rating,
          mypar
        )
      )
      model = lmer(myformula, data = ratingdata %>% filter(context_order == co))
      ss = summary(model)
      print(myformula)
      print(ss)
      ss.1 = coef(ss)[sprintf("scale(%s)", mypar), c("Estimate", "t value", "df", "Pr(>|t|)")]
      ss.2 = coef(ss)[sprintf("scale(%s):scale(amount_later)", mypar), c("Estimate", "t value", "df", "Pr(>|t|)")]
      main.mat = rbind(main.mat, c(mypar.rating, mypar, co, round(ss.1, 3)))
      inter.mat = rbind(inter.mat, c(mypar.rating, mypar, co, round(ss.2, 3)))
    }
    
    ratingdata.subj = ratingdata %>% group_by(subjID, Context, Context_order) %>% summarise_at(c(mypars, mypars.rating), .funs = 'mean')
    
    myplot.rating.pars = ggplot(data = ratingdata.subj,
                                aes_string(
                                  y = mypar.rating,
                                  x = mypar,
                                  color = 'Context',
                                  group = 'subjID'
                                )) +
      #  geom_line(size = 0.5, alpha = 0.4) +
      #  geom_point(size = 0.5, alpha = 0.4) +
      geom_line() +
      geom_point() +
      xlab(choice_par_names[mypar]) +
      ylab(rating_par_names[mypar.rating]) + facet_grid(. ~ Context_order)
    print(myplot.rating.pars)
    myplots.list[[j]]  = myplot.rating.pars
    j = j + 1
  }
}
main.mat = as.data.frame(main.mat)
inter.mat = as.data.frame(inter.mat)
main.mat = main.mat %>% arrange(V1, V3, V2)
inter.mat = inter.mat %>% arrange(V1, V3, V2)
main.mat = main.mat %>% mutate(V1 = rating_par_names[as.character(V1)], V2 = choice_par_names[as.character(V2)])
inter.mat = inter.mat %>% mutate(V1 = rating_par_names[as.character(V1)], V2 = choice_par_names[as.character(V2)])

colnames(main.mat) = colnames(inter.mat) = c("WTP parameter",
                                             "DDM parameter",
                                             "Context order",
                                             "Estimate",
                                             "t",
                                             "df",
                                             "p-value")
View(main.mat)
View(inter.mat)

#myplot.main.intercept = ggplot(ratingdata, aes(x = jitter(amount_later), y = b.drift.intercept.p, col = bid.diff )) + geom_point() + scale_color_viridis_c()
#print(myplot.main.intercept)
#myplot.main.amount = ggplot(ratingdata, aes(x = jitter(amount_later), y = b.drift.amount.p, col = bid.diff )) + geom_point() + scale_color_viridis_c()
#print(myplot.main.amount)
statslist['_table_range_main_'] = tab_to_str(main.mat)
statslist['_table_range_inter_'] = tab_to_str(inter.mat)

#ratingdata.melt = melt(ratingdata, measure.vars = mypars.rating, variable.name = "Parameter")

```


# Mediation of DDM parameters

```{r}
#source('./Mediations.R')
```


# Parameter tests
```{r, fig.width = 15}
source('./ParameterAnalysis.R')
```



```{r, fig.width = 15}
# Standard error of the mean
myplot = ggplot(allIndPars.sum, aes(x=parameter, y=value)) + 
    geom_errorbar(aes(ymin = value-se, ymax = value+se), width=.1) +
    geom_line() +
    geom_point() + 
    ylab('Parameter difference (low volatility - high volatility)') + 
    geom_hline(yintercept = 0, col = 'red')
print(myplot)

```

# Check correlation between parameters

```{r, fig.width = 15}
options(width = 300)

mydata = allIndPars %>% filter(subjID %in% include_subjects  &
                                 nondectime.p < 2)
cor(mydata[mypars])
pairs(mydata[mypars])

mydata = mydata %>% mutate(
  Context_tag = ifelse(Context_short == 'High', 'HV', 'LV'),
  Group_tag = ifelse(Group == 'High vol. first', 'HF', 'LF')
)

mydata$GroupContext = paste(mydata$Group_tag, mydata$Context_tag, sep = " - ")

myplot.pairs <-
  ggpairs(
    mydata,
    columns = mypars,
    ggplot2::aes(colour = GroupContext),
    columnLabels = par_labels,
    upper = list(continuous = wrap("cor", size = 3.5))
  ) +
  theme (strip.text = element_text (size = 12))
print(myplot.pairs)

```



```{r}


HEIGHT1ROW = 4.06
WIDTH1COL = 3.8
DPI = 1000

FIGS_DIR = '../figs'

#myplot.trial.RT

fig.a.1 = ggarrange(
  myplot.RT.choice.group,
  myplot.RT.choice.agg,
  ncol = 2,
  nrow = 1,
  labels = c('A', 'B')
)
fig.a.2 = ggarrange(
  myplot.trial.RT,
  ncol = 1,
  nrow = 1,
  labels = c('C')
)
fig.a.3 = ggarrange(
  myplot.choiceprob.group,
  myplot.choiceprob.agg,
  ncol = 2,
  nrow = 1,
  labels = c('D', 'E')
)

fig.a.4 = ggarrange(
  myplot.choiceprob.diff.group,
  myplot.choiceprob.diff.agg,
  ncol = 2,
  nrow = 1,
  labels = c('F', 'G')
)

# 
# fig.a.2 = ggarrange(
#   myplot.RT.choice.group,
#   myplot.RT.choice.agg,
#   myplot.choiceprob.group,
#   ncol = 3,
#   nrow = 1,
#   labels = c('B', 'C', 'D')
# )
# fig.a.3 = ggarrange(
#   myplot.choiceprob.agg,
#   myplot.choiceprob.diff.group,
#   myplot.choiceprob.diff.agg,
#   ncol = 3,
#   nrow = 1,
#   labels = c('E', 'F', 'G')
# )
# 

# fig.a = ggarrange(myplot.RT.choice.group, myplot.RT.choice.agg,
#                    myplot.choiceprob.group, myplot.choiceprob.agg,
#                    ncol=2, nrow=2, labels = c('A', 'B', 'C', 'D'))

fig.a.l = ggarrange(fig.a.2, fig.a.3, fig.a.4,
                  ncol = 3, nrow = 1)

fig.a = ggarrange(fig.a.1, fig.a.2, fig.a.3, fig.a.4,
                   ncol = 1, nrow = 4)

#fig.a = ggarrange(fig.a.1, fig.a.l,
#                  ncol = 1, nrow = 2, heights = c(1, 2))

# fig.a = ggarrange(fig.a.1, fig.a.2, fig.a.3, 
#                   ncol = 1, nrow = 3)

ggsave(
  filename = file.path(FIGS_DIR, "Choices.png"),
  plot = fig.a,
  dpi = DPI,
  width = WIDTH1COL * 2,
  height = HEIGHT1ROW * 3
)

fig.b = ggarrange(
  myplot.differences.all,
  myplot.differences.agg,
  ncol = 1,
  nrow = 2,
  labels = c('A', 'B')
)
#fig.a = ggarrange(fig.a1, fig.a2, ncol=1, nrow=2, heights = c(1, 1))

ggsave(
  filename = file.path(FIGS_DIR, "Parameters.png"),
  plot = fig.b,
  dpi = DPI,
  width = WIDTH1COL * 2,
  height = HEIGHT1ROW * 2
)


fig.c = ggarrange(
  myplot.range.group,
  myplot.range.agg,
  myplot.key.rt.group,
  myplot.key.rt.agg,
  ncol = 2,
  nrow = 2,
  labels = c('A', 'B', 'C', 'D')
)
ggsave(
  filename = file.path(FIGS_DIR, "Ratings.png"),
  plot = fig.c,
  dpi = DPI,
  width = WIDTH1COL * 2,
  height = HEIGHT1ROW * 2
)

fig.d = ggarrange(plotlist = myplots.list,
                  ncol = 6,
                  nrow = 2)

ggsave(
  filename = file.path(FIGS_DIR, "Associations.png"),
  plot = fig.d,
  dpi = DPI,
  width = WIDTH1COL * 5,
  height = HEIGHT1ROW * 2
)

ggsave(
  filename = file.path(FIGS_DIR, "ParameterCorrelations.png"),
  plot = myplot.pairs,
  dpi = DPI,
  width = WIDTH1COL * 2,
  height = HEIGHT1ROW * 2
)

print(fig.a)
print(fig.b)
print(fig.c)
print(fig.d)

if (init100) {

fig.e = ggarrange(
  myplot.RT.choice.group,
  myplot.RT.choice.agg,
  myplot.choiceprob.group,
  myplot.choiceprob.agg,
  myplot.choiceprob.diff.group,
  myplot.choiceprob.diff.agg,
  ncol = 2,
  nrow = 3,
  labels = c('A', 'B', 'C', 'D', 'E', 'F')
)


ggsave(
  filename = file.path(FIGS_DIR, "Choices_100.png"),
  plot = fig.e,
  dpi = DPI,
  width = WIDTH1COL * 2,
  height = HEIGHT1ROW * 3
)

print(fig.e)
}

```



Table for the regressions
```{r}

reg_labels = c(
  "(Intercept)" =  "Intercept",                                                    
  "GroupLow vol. first"= "Group (low volatility first)",
  "ContextLow volatility"= "Context (low volatility)",                            
  "amount_later_centered" = "Later reward (centered)", 
  "amount_later_centered.2" = "Later reward (centered) squared", 
  "background_colpurple" = "Background color (purple)",
  "background_colteal" = "Background color (teal)", 
  "GroupLow vol. first:ContextLow volatility" = "Group (low volatility first) x context (low volatility)",    "ContextLow volatility" = "Context (low volatility)",
  "GroupLow vol. first:amount_later_centered" = "Group (low volatility first) x later reward (centered)",
  "ContextLow volatility:amount_later_centered" = "Context (low volatility) x later reward (centered)",
  "GroupLow vol. first:ContextLow volatility:amount_later_centered" = "Group (low volatility first) x later reward (centered)",
  "ChoiceLater option"= "Choice (later option)",
  "ChoiceLater option:amount_later_centered" = "Choice (later option) x later reward (centered)",
  "ChoiceLater option:amount_later_centered.2" = "Choice (later option) x later reward (centered) squared"
)

choice.labels = unlist(reg_labels[rownames(choice.fixef)])
rt.labels = unlist(reg_labels[rownames(rt.fixef)])
rt.cor.labels = unlist(reg_labels[rownames(rt.cor.fixef)])
choice.fixef = apply(choice.fixef, 2, reformat)
choice.fixef = as.data.frame(choice.fixef)

colnames(choice.fixef) =  c(
 "Estimate",
 "Sd",    
 "z",
 "p-value")

choice.fixef = data.frame(Parameter = choice.labels, choice.fixef)

rt.fixef = apply(rt.fixef, 2, reformat)
rt.cor.fixef = apply(rt.cor.fixef, 2, reformat)
rt.fixef = as.data.frame(rt.fixef)
rt.cor.fixef = as.data.frame(rt.cor.fixef)
colnames(rt.fixef) = colnames(rt.cor.fixef) =  
c(
 "Estimate",
 "Sd",    
 "df",
 "t",
 "p-value")
rt.fixef = data.frame(Parameter = rt.labels, rt.fixef)
rt.cor.fixef = data.frame(Parameter = rt.cor.labels, rt.cor.fixef)

statslist['_table_choice.fixef_'] = tab_to_str(choice.fixef[, c(1,2,4,5)])
statslist['_table_rt.fixef_'] = tab_to_str(rt.fixef[, c(1,2,5,4,6)])
statslist['_table_rt.cor.fixef_'] = tab_to_str(rt.cor.fixef[, c(1,2,5,4,6)])
```



```{r}
filein = '../results/results_text_noise.txt'
fileout = ifelse(!init100, 
  '../results/results_text_fixed_noise.txt',
  '../results/results_text_fixed_noise_100.txt')

text = readLines(filein)
print(statslist)
text.new = NULL
placeholders = names(statslist)
for (line in text){ 
for (placeholder in placeholders){
  line = gsub(placeholder, replacement = statslist[placeholder], line)
}
text.new = c(text.new, line)

}
unlink(fileout)
writeLines(text.new, con = fileout)
```

